---
title: ""
author:
  -"Sumedh R. Sankhe"
  -"Shivayogi Biradar"
  -"Sharyu Deshmukh"
  -"Mania Abdi"
date: ""
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
  header-includes:
  toc: true
  fig.caption: true
---


\centering
\centerline{\includegraphics[height=2in]{C:/Users/Sumedh/Documents/Northeastern_University/DS5110_Data_Processing_Data_Management/nu.png}}

#Northeastern University  
####College of Computer and Information Science 
####DS-5220 : Supervised Machine Learning and Learning Theory  
####Spring 2017
####Predicting House Prices using the Ames IA dataset



\raggedright

\clearpage


\tableofcontents
\newpage  
```{r, setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(readr)
library(knitr)

knitr::opts_chunk$set(
  tidy=FALSE,# display code as typed
  warning = FALSE,#do not display any warning messages
  message = FALSE,
  size="small")   # slightly smaller font for code
```

#Introduction:

\newpage
#Methods:

\newpage
#Results:

\newpage
#References:

\newpage
#Appendix:

```{r, warnings=FALSE}
test <- read_csv("test.csv")
train <- read_csv("train.csv")


plot.na <- function(x){
  na_count <- sapply(x, function(y) sum(length(which(is.na(y)))))
  na_df <- data.frame(keyName = names(na_count),
                      value = na_count, 
                      row.names = NULL)
  
  #Visualizing the missing values
  na_df%>%
    arrange(desc(value))%>%
    head(n=20)%>%
    ggplot(aes(x = reorder(keyName,value),
               y = value,
               fill = value))+
    labs(x = "Feature",
         y = "Missing Count",
         title = paste("Visualizing Missing Value Count",deparse(substitute(x)),"data"))+
    geom_bar(stat = "identity")+
    coord_flip()
}


plot.na(train)
plot.na(test)
```


```{r}
#Looking at each neighborhood and figuring out which neighborhood 
test%>%
  filter(Neighborhood == "IDOTRR")%>%
  group_by(Neighborhood,Functional)%>%
  count()%>%
  ggplot(aes(x=Functional,
             y = n))+
  geom_bar(stat = "identity")

test$Functional[is.na(test$Functional)] <- "Typ"

test%>%
  filter(Neighborhood == "Edwards")%>%
  group_by(Exterior1st)%>%
  count()%>%
  ggplot(aes(x = reorder(Exterior1st,n),
             y = n))+
  geom_bar(stat = "identity",
           position = "dodge")+
  labs(x = "Exterior 1st",
       y = "Count")+
  coord_flip()

test$Exterior1st[is.na(test$Exterior1st)] <- "Wd Sdng"

test%>%
  filter(Neighborhood == "Edwards")%>%
  group_by(Exterior2nd)%>%
  count()%>%
  ggplot(aes(x = reorder(Exterior2nd,n),
             y = n))+
  geom_bar(stat = "identity",
           position = "dodge")+
  labs(x = "Exterior 1st",
       y = "Count")+
  coord_flip()
test$Exterior2nd[is.na(test$Exterior2nd)] <- "Wd Sdng"

#After going through the datasheet provided by the competition it was found that NA in the following columns depicted no basements hence 0 was substitued.
test$TotalBsmtSF[is.na(test$TotalBsmtSF)] <- 0
test$BsmtFinSF1[is.na(test$BsmtFinSF1)] <- 0
test$BsmtFinSF2[is.na(test$BsmtFinSF2)] <- 0
test$BsmtUnfSF[is.na(test$BsmtUnfSF)] <- 0
test$BsmtFullBath[is.na(test$BsmtFullBath)] <- 0
test$BsmtHalfBath[is.na(test$BsmtHalfBath)] <- 0

```





```{r}
#' This function converts NA values of continuous variables to Mean
impute.mean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))

#' This function converts NA values of continuous variables to median
impute.median <- function(x) replace(x,is.na(x), median(x,na.rm = TRUE))


test%>%
  filter(is.na(LotFrontage))%>%
  group_by(Neighborhood)%>%
  count()%>%
  ggplot(aes(x = Neighborhood,
             y = n))+
  geom_bar(stat = "identity")+
  coord_flip()

test%>%
  filter(is.na(GarageYrBlt))%>%
  group_by(Neighborhood)%>%
  count()%>%
  ggplot(aes(x = Neighborhood,
             y = n))+
  geom_bar(stat = "identity")+
  labs(x = "Count of NA",
       title = "NA vs Neighborhoods for GarageYrBlt")+
  coord_flip()

test%>%
  group_by(Neighborhood)%>%
  mutate(LotFrontage = impute.mean(LotFrontage),
         GarageYrBlt = impute.median(GarageYrBlt),
         MasVnrArea = impute.median(MasVnrArea),
         GarageCars = impute.median(GarageCars))->test

train%>%
  group_by(Neighborhood)%>%
  mutate(LotFrontage = impute.mean(LotFrontage),
         GarageYrBlt = impute.median(GarageYrBlt),
         MasVnrArea = impute.median(MasVnrArea),
         GarageCars = impute.median(GarageCars))-> train


plot.na(test)
```  


```{r}
#This function converts all columns of class character in a dataframe to a factor and fills NA and None with No
convert.factor <- function(x){
  char1 <- x[, sapply(x, class) == 'character']
  not_char <- x[, sapply(x, class) != 'character']
  char1 <- as.data.frame(
  t(
    apply(char1,1,function(y)ifelse(is.na(y),"No",ifelse(y=="None","No",y)))))
  char1 <- as.data.frame(unclass(char1))
  x <- cbind.data.frame(char1,not_char)
  return(x)
}


#This function creates histograms for continuous data and barplots for categorical data
dfplot <- function(df)
{
  ln <- length(names(df))
  for(i in 1:ln){
    mname <- substitute(df[,i])
      if(class(df[,i])=="factor"){
        plot(df[,i],
             main=paste("Histogram of",colnames(df)[i]),
             xlab = colnames(df)[i])}
        else{hist(df[,i],
                  main=paste("Histogram of",colnames(df)[i]),
                  xlab = colnames(df)[i])}
  }
}

```

\newpage
#Statement of Contributions:

